### 2020-03-11 README.Rmd
containment and band creation outside ternary visual. convex hull has problems - need to project to simplex space (which is annoying - especially given that we haven't been thinking about that project for the delta ball approach).

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  dpi = 120
)
```

@@

## Notes:
1. For writing code that works with `tidyverse` 1.0 vs `tidyverse` <= 0.8.3. We followed ideas found in [tidyr: in-packages](https://tidyr.tidyverse.org/articles/in-packages.html), for the code, and - when working with Travis CI (using a matrix for multiple builds) - we leverage ideas in [tidyverse travis on github](https://github.com/tidyverse/design/issues/95) and [tidyverse principles](https://principles.tidyverse.org/changes-multivers.html).
2. For writing your own `geom`s and `stat`s that works with `ggtern` (which are generally restricted), the following 2 stack-exchange articles helped use do so with ease:
    a. [stack-exchange: personal code idea](https://stackoverflow.com/questions/57175114/ternary-plot-scaling-opacity-across-groups)
    b. [stack-exchange: being able to access ggtern's element write away](https://stackoverflow.com/questions/31589479/how-to-fix-no-item-called-packagepkg-on-the-search-list-without-using-libra#comment51172891_31589479)
    c. Finally, we've also leveraged ideas from [R-devel: on avoiding problems with `:::`](https://stat.ethz.ch/pipermail/r-devel/2013-August/067210.html) in `R/aaa.R` to overcome messages from CRAN relative to this hack (using `:::`). For some reason - when documenting for `pkg-down` website, we need to do `library(ggtern); timeternR:::update_approved_layers()`

>>>>

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  dpi = 300
)
```

@@

## Notes:
1. For writing code that works with `tidyverse` 1.0 vs `tidyverse` <= 0.8.3. We followed ideas found in [tidyr: in-packages](https://tidyr.tidyverse.org/articles/in-packages.html), for the code, and - when working with Travis CI (using a matrix for multiple builds) - we leverage ideas in [tidyverse travis on github](https://github.com/tidyverse/design/issues/95) and [tidyverse principles](https://principles.tidyverse.org/changes-multivers.html).
2. For writing your own `geom`s and `stat`s that works with `ggtern` (which are generally restricted), the following 2 stack-exchange articles helped use do so with ease:
    a. [stack-exchange: personal code idea](https://stackoverflow.com/questions/57175114/ternary-plot-scaling-opacity-across-groups)
    b. [stack-exchange: being able to access ggtern's element write away](https://stackoverflow.com/questions/31589479/how-to-fix-no-item-called-packagepkg-on-the-search-list-without-using-libra#comment51172891_31589479)
    c. Finally, we've also leveraged ideas from [R-devel: on avoiding problems with `:::`](https://stat.ethz.ch/pipermail/r-devel/2013-August/067210.html) in `R/aaa.R` to overcome messages from CRAN relative to this hack (using `:::`). For some reason - when documenting for `pkgdown` website, we need to do `library(ggtern); timeternR:::update_approved_layers()`
